The Name of the Title is Hope

### 2020-03-18 paper.tex
Some changes

\section{Template Overview}
As noted in the introduction, the ``\verb|acmart|'' document class can
be used to prepare many different kinds of documentation --- a
double-blind initial submission of a full-length technical paper, a
two-page SIGGRAPH Emerging Technologies abstract, a ``camera-ready''
journal article, a SIGCHI Extended Abstract, and more --- all by
selecting the appropriate {\itshape template style} and {\itshape
  template parameters}.

This document will explain the major features of the document
class. For further information, the {\itshape \LaTeX\ User's Guide} is
available from
\url{https://www.acm.org/publications/proceedings-template}.

\section{Method}
% --- COPIED FROM ABSTRACT ASSIGNMENT --- %
% Explain your study design, illustrate how the study's results will provide
% evidence for/against your hypothesis, and how the question, hypothesis, and
% study all line up. We encourage you to mirror/copy/adapt other researchers
% methods (e.g. by drawing from the class readings) whenever appropriate (and
% not when it isn't appropriate).

@@

% Measures:
% How will you know you succeeded? What will you measure? How will you measure
% it? What might your results look like?

% Ecological Validity:
% Why does your study answer your research question? Why
% does your evaluation address your hypothesis? Make sure your study, and the
% variables you're measuring, properly address the question you are asking.
\subsection{Measures}
% We expected to see that examples increased the speed of candidate selection
% with little to no loss in accuracy.
% %
% Furthermore we expected that speedup to be explained by decreased reliance on
% the interpreter.
% %
% Specifically, users should no longer need to run their own input-output tests
% on the candidate programs.

For each participant, we measured:
\begin{itemize}
    \item Time-to-correct solution (per task)
    \item Count of incorrect guesses (per task)
    \item Count and type of interpreter queries (across all tasks)
\end{itemize}

>>>>

\section{Method}

% --- COPIED FROM ABSTRACT ASSIGNMENT --- %
% Explain your study design, illustrate how the study's results will provide
% evidence for/against your hypothesis, and how the question, hypothesis, and
% study all line up. We encourage you to mirror/copy/adapt other researchers
% methods (e.g. by drawing from the class readings) whenever appropriate (and
% not when it isn't appropriate).

@@

% Ecological Validity:
% Why does your study answer your research question? Why
% does your evaluation address your hypothesis? Make sure your study, and the
% variables you're measuring, properly address the question you are asking.
\subsection{Measures}
For each participant, we measured:
\begin{itemize}
    \item Time-to-correct solution (per task)
    \item Count of incorrect guesses (per task)
    \item Count and type of interpreter queries (across all tasks)
\end{itemize}
